On Extending a Full-Sharing Multithreaded Tabling Design with Batched Scheduling

### 2015-05-26 paper.tex
paper -> revising 1

We have presented a simple and novel approach for combining the FS
design with batched scheduling. Experimental results showed that on
average, the extra structures required for the combination do not seem
to have a big impact in the performance. Further work will include
experimentation in other real world applications.

@@

This work is partially funded by the ERDF (European Regional
Development Fund) through the COMPETE Programme and by FCT (Portuguese
Foundation for Science and Technology) within projects SIBILA
(NORTE-07-0124-FEDER-000059) and PEst
(FCOMP-01-0124-FEDER-037281). Miguel Areias is funded by the FCT grant
SFRH/BD/69673/2010.

>>>>

Local and batched scheduling are arguably two of the most well-known
tabling scheduling techniques. The major difference between them is
that local propagates answers only after all answer are found, while
batched propagates answers immediately after they are found. Batched
scheduling is a useful strategy in tabled logic programs that require
an eager propagation of answers and/or do not require the complete set
of answers to be found (partial evaluation of the search space).

In this work, we have presented the PAC strategy, which is a simple
and novel approach for combining the FS design with batched
scheduling. PAC splits answer representation from answer propagation,
allowing the first to be publicly shared among threads while the
second is private to each thread.

Experimental results in worst-case scenarios showed that on average,
the PAC strategy does not seem to have a big impact in the
performance, however it still leaves room for further improvements
specially in the extra structures required to control the propagated
answers. Further work will include the usage of time-stamped tries to
minimize the search for the propagated answers and new real-world
problems that will allow us to improve and consolidate our framework.

@@

%% This work is partially funded by the ERDF (European Regional
%% Development Fund) through the COMPETE Programme and by FCT (Portuguese
%% Foundation for Science and Technology) within projects SIBILA
%% (NORTE-07-0124-FEDER-000059) and PEst
%% (FCOMP-01-0124-FEDER-037281). Miguel Areias is funded by the FCT grant
%% SFRH/BD/69673/2010.
